Recursive Solutions to First-Order Model Counting

### 2022-02-21 notes/notes.tex
All experimental results

For both one domain and two domains:
\begin{itemize}
\item bijections
\item injections
\item partial injections
\end{itemize}

>>>>

\textsc{ForcLift} fails on all of these.

\paragraph{TODO.}
\begin{itemize}
\item Explain the algebraic notation that I'm using here (e.g., that $f$ is always the main function)
\item Explain the Knuth's bracket notation (or use something else, since I'm already using brackets for lists)
\item Explain the importance of comparing domain sizes to 2.
\item Maybe a big table: name, formula, optimal solution and its complexity, best found solution, its depth, its complexity. Also mention that it only takes a few seconds to find these solutions.
\item Have at least one example of how an FCG maps to recursive functions
\item Going beyond depth 6 (or sometimes even completing depth 6) is computationally infeasible with the current implementation, but depth at most 5 can be searched within at most a few seconds.
\end{itemize}

\begin{itemize}
\item 1d bijections and 1d injections (note that it's the same problem). Depth 3 solution:
  \begin{align*}
    f(n) &= \sum_{m=0}^n \binom{n}{m} (-1)^{n-m}g(n, m) \\
    g(n, m) &= \sum_{l=0}^n \binom{n}{l}[l < 2]g(n-l, m-1) \\
    &= g(n, m - 1) + ng(n - 1, m - 1),
  \end{align*}
  which works with base case $g(n, 0) = 1$.
\item 1d partial injections. 2 solutions at depth 6, but they're too complicated to check by hand. A contradiction with $X \ne x$ constraints makes things complicated.
\item 2d bijections. Depth 3:
  \begin{align*}
    f(m, n) &= \sum_{l=0}^m \binom{m}{l} [l < 2] (1 - [l < 1])f(m-l, n-1) \\
    &= mf(m-1, n-1),
  \end{align*}
  which works with base cases $f(0, 0) = 1$, $f(0, n) = 0$, $f(m, 0) = 0$.
\item 2d injections. Depth 2:
  \begin{align*}
    f(m, n) &= \sum_{l=0}^m \binom{m}{l}[l<2]f(m-l, n-1) \\
    &= f(m, n-1) + mf(m-1, n-1),
  \end{align*}
  which works with base cases $f(0, 0) = 1$ and $f(m, 0) = 0$.
\item 2d partial injections, depth 2. Exactly the same circuit as above but with base case $f(m, 0) = 1$.
\end{itemize}
